Fractional Types

### 2019-11-23 fracGC/p.tex
the extracted program is reversible only if there is no fraction on type

The program takes a value of type
\Acon{∙𝟙/}~(\Acon{∙𝟙/}~\Avar{A}). This would be a gc process
specialized to collect another gc process! At runtime, there would
be no information other than the functions that ignore their argument
but the type system provides enough guarantees to ensure that this
process is well-defined, is reversible, and is safe. The following
trace shows the actual execution for confirmation:

>>>>

The program takes a value of type
\Acon{∙𝟙/}~(\Acon{∙𝟙/}~\Avar{A}). This would be a gc process
specialized to collect another gc process! At runtime, there would
be no information other than the functions that ignore their argument
but the type system provides enough guarantees to ensure that this
process is well-defined and safe. The following
trace shows the actual execution for confirmation:
